Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ \smaller \textbf{{London version \YellowPaperVersionNumber}}

### 2023-11-08 Paper.tex
grammar edits and clarifications

\begin{description}
  \item[maxFeePerGas]\linkdest{max_fee_per_gas}{} A scalar value equal to the maximum number of Wei to be paid per unit of \textit{gas} for all computation costs incurred as a result of the execution of this transaction; formally $T_{\mathrm{m}}$.
  \item[maxPriorityFeePerGas]\linkdest{max_priority_fee_per_gas}{} A scalar value equal to the maximum number of Wei to be paid to the block's fee recicipient as an incentive to include the transaction; formally $T_{\mathrm{f}}$.
\end{description}

@@

The total refundable amount is the legitimately remaining gas $g'$, added to \hyperlink{refund_balance_defn_words_A__r}{$A_{\mathrm{r}}$}, with the latter component being capped up to a maximum of one fifth\footnote{The max refundable proportion of gas was changed by EIP-3529 by \cite{EIP-3529}} (rounded down) of the total amount used $T_{\mathrm{g}} - g'$. Therefore, $g^*$ is the total gas that remains after the transaction has been executed.

@@

>>>>

\begin{description}
  \item[maxFeePerGas]\linkdest{max_fee_per_gas}{} A scalar value equal to the maximum number of Wei to be paid per unit of \textit{gas} for all computation costs incurred as a result of the execution of this transaction; formally $T_{\mathrm{m}}$.
  \item[maxPriorityFeePerGas]\linkdest{max_priority_fee_per_gas}{} A scalar value equal to the maximum number of Wei to be paid to the block's fee recipient as an incentive to include the transaction; formally $T_{\mathrm{f}}$.
\end{description}

@@

The total refundable amount is the legitimately remaining gas $g'$, added to \hyperlink{refund_balance_defn_words_A__r}{$A_{\mathrm{r}}$}, with the latter component being capped up to a maximum of one fifth\footnote{The max refundable proportion of gas was reduced from one half to one fifth by EIP-3529 by \cite{EIP-3529} in the \textit{London} release} (rounded down) of the total amount used $T_{\mathrm{g}} - g'$. Therefore, $g^*$ is the total gas that remains after the transaction has been executed.

@@

Note the last condition of $F$ indicates that contract code cannot begin with the byte \texttt{0xef} (refer to EIP-3541 by \cite{EIP-3541}),
